Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-05 writeup/gz_hubble_data.tex
Text changes and tightening of language.

The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria. The majority of the data (as implied by the project name) are taken directly from \hst{} Legacy Surveys, all of which primarily use imaging from the Advanced Camera for Surveys (ACS). A summary of the key parameters is given in Table~\ref{tbl:gzh_numbers}.

@@

In the Advanced Camera for Surveys General Catalog \citep[ACS-GC;][]{gri12}, individual galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \galapagos{} \citep{bar12}. GZH includes all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).

@@

Since the majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only 1 or 2~bands available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo was not possible. For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band is mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two. Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).

@@

To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask is applied to the image that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky. This technique was applied only to the coadded Stripe~82 and the COSMOS images.

@@

GZH also includes a set of images designed to measure the effect of active galactic nuclei (AGN) on morphological classifications. Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic or distort the identification of a bulge component. The presence of an AGN is simulated by modeling the PSF for \hst{} and then inserting a bright source near the center of a real galaxy. For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generates 15~images with different simulated AGN for each host.

@@

For galaxies which have published redshifts from multiple sources, the following algorithm is used to select the $\tt Z\_BEST$ quantity. This first priority is spectroscopic redshifts; these are provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A high quality spectroscopic redshift in the ACS-GC is the primary option; if none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more than 98\% are consistent at $\Delta z<0.001$; therefore, the priority order of selection makes no negligible difference for the sample. If no spectroscopic redshifts are available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift with the smallest error. Table~\ref{tbl:redshifts} shows the results of this selection.

@@

Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken from the CasJobs DR7 tables. This includes $ugriz$ Petrosian magnitudes and fluxes, as well as the relative de~Vaucouleurs and exponential fits from the model magnitudes. Redshifts used for the Sloan galaxies are all spectroscopic. 82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the coadd images have a measured DR7 spectroscopic redshift.

@@

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshfts with those at the lowest redshift. See \citet{bam09} and \citet{wil13} for the details.

@@

%The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
The surface brightness selection ($N_\mu = 3$) for the FERENGI galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts'' ($z = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z=1.0$.

@@

\begin{table}
\caption{Summary of FERENGI artificial redshifting \label{tbl:ferengivalues}}
\begin{tabular}{lccccr}
\hline\hline
$z_{\rm target}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
\hline
0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
\hline\hline
\end{tabular}
\end{table}

@@

The change in bias as a function of $\mu_r$ and $z$ is measured using the \ferengi{} images over all the evolutionary correction factors. It is assumed that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:

@@

GZH uses the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies to fit the overall distribution as a function of surface brightness, since the correction being applied is expected to vary as a function of the intrinsic galaxy properties. The galaxies that can be used to measure the calibration are restricted to those with data at the pivot redshift of $z=0.3$, non-zero $f_\textrm{features}$ at $z=0.3$, and with a reasonable fit to the exponential model ($\Delta \chi^2 > 3.0$).

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
\caption{Surface brightness vs. redshift of 118,083 galaxies in the ACS sample. The white grid denotes the surface brightness and redshift range of the \ferengi{} images, subdivided in bins corresponding to fixed ranges used for analysis in Figure~\ref{fig:p_vs_p}.}
\label{fig:sb_redshift}
\end{center}
\end{figure}

@@

Figure~\ref{fig:p_vs_p} shows that the relationship between \pfeaturesz{} and \pfeaturesrest{} is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/\pfeatures{} space. These regions tend to have low \pfeatures{} values at high redshift, but a wide range of values at $z=0.3$. These regions contain two morphological types of galaxies: First are genuine ellipticals, which have low values of \pfeatures{} at both high and low redshift. Second are disks whose features become washed out at high redshift; hence their \pfeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low. This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.

The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \pfeaturesz{} and \pfeaturesrest{} is modeled by fitting the data with a polynomial of degrees 3, 2, and 1, and use the best fit out of the three. These fits are shown as the dashed black lines in Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; this is quantified by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \pfeaturesz{} cannot be boosted to its \pfeaturesrest{} value. Galaxies in this region are referred to as the \emph{lower limit} sample. These regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently high slopes to consider the relationship as single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies are considered to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the $\zeta$ approach to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \pfeatures{}. To define this smooth space, a convex hull is generated that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. The resulting hulls define the correctable and lower-limit regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than $z=z_{0}=0.3$, 17\% of these are able to be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot be determined, due to a lack of redshift or information or due to a lack of \ferengi{} data corresponding to those galaxies' redshift/surface brightness values.

@@

\subsection{Challenges of debiasing questions beyond ``smooth or features''}
\label{ssec:higher_order_tasks}
As with the HST images, each FERENGI subject has a varying number of users answering the various questions in the hierarchical decision tree. Every user answers the first question, ``Is the galaxy smooth and rounded, with no sign of a disk?''; as such the vote fractions $\rm p_{smooth}, p_{features}$, and $\rm p_{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}). The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question. The average number of responses per task for fourth- or fifth-tier questions such as spiral arm structure (Tasks 12--14) is only $4\pm4$ for the FERENGI sample; while this is distribution is strongly bimodal (reflecting the true morphologies of selected galaxies), the very low absolute numbers of votes introduce very high variance when attempting to calculate a statistical correction.

@@

\begin{figure*}
\center
\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full GZH sample. The lower-limit galaxies have higher redshifts, slightly lower surface brightness, and lower values of $p_{features}$ on average than the correctable galaxies. The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
\label{fig:z_mu_p}
\end{figure*}

@@

\section{The catalog}\label{sec:results}

The data release for GZH includes morphological data for 181,101~images (generated from a total of 150,771~unique galaxies). The full table can be accessed at \url{http://data.galaxyzoo.org}. This also includes a secondary metadata table, which contains data from a variety of sources explained in Section \ref{sec:data}.

@@

The GZH catalog is corrected for classification bias in the first question of the GZH decision tree, which asks ``Is the galaxy smooth and round, with no sign of a disk?'' The method is described in Section~\ref{sec:debiasing}. For this question, the catalog provides the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if a lower limit, $\tt best = lower~limit$, and if neither, $\tt best = weighted$.

The debiased and best vote fractions for $\tt p_{smooth}$ were calculated on the critera that vote fractions for all answers must sum to unity. Explicitly: $\tt p_{smooth} = 1 - p_{features} - p_{artifact}$. In some rare cases, representing  $<1\%$ of the sample, this requirement resulted in negative vote fractions for $\rm p_{smooth}$; these were cases in which the $\rm p_{features}$ vote fraction was boosted to a high value relative to the $\rm p_{artifact}$ vote fraction. In these cases, the constraint that the vote fractions must sum to 1 is met by raising $\rm p_{smooth}$ to a vote fraction of 0.0 and decreasing $\rm p_{features}$ accordingly. This correction is typically small, with a median decrease/increase of $\rm p_{features}/p_{smooth}$ of $\Delta p = 0.04$.

@@

In GZH, volunteers answer questions about a galaxy's morphology in a decision tree format. With this structure, questions shown to a user are dependent on their answers to the previous questions. For example, a user is only asked Task 11, ``How many spiral arms?'' if they had answered ``yes'' to Task 10, which asks whether any spiral arms are present. This structure is used to reduce the workload of the users by only asking questions relevant to the particular galaxy; in this example, it would not be useful, nor would it make physical sense, to ask a user how many spiral arms in a galaxy which they had declared had no spiral arms to begin with. Figure~\ref{fig:decisiontree} shows the possible paths available for answering the questions offered in GZH. The colors represent the tier level of Tasks, which indicate the number of previous Tasks the given Task is dependent upon. The arm-number question, Task 11, is a 5th tier Task, meaning that whether this question is seen by a user is dependent on four Tasks preceding it. In this case, it is only shown to volunteers who voted the galaxy was featured/disk-shaped in Task 01, not clumpy in Task 12, not edge-on in Task 02, and had spiral structure in Task 10.

@@

{\note \it Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc. Briefly discuss results as compared with literature and theory.}

@@

The second set of plots in Figure~\ref{fig:comparisons} indicates that \podd{} is largely an effective method for separating irregular and/or peculiar galaxies from spirals. Despite the somewhat vague wording of the ``anything odd?'' question in GZH, the AEGIS, COSMOS, and GOODS all show a marked increase in the irregular fraction increasing with \podd. Any threshold value for distinguishing between the two, however, depends strongly on survey/redshift~range.

@@

Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample. Figure~\ref{fig:shallow_vs_full} shows a strong correlation between $\rm p_{features}$ for both sets of images. The mean change in $\rm p_{features}$ from the shallow to full depth images  $\rm p_{features,full} - p_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$. While there is some variance in $\Delta p$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification. Defining a clean sample of disk galaxies as those with $p_{features,best}>0.8$, elliptical galaxies as those with  $p_{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology. Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or visa versa, while the rest would transition to or from the ``intermediate'' morphology. Details can be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images representing the 9 possible changes (or lack of) in morphology are shown in Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and \ref{fig:shallow_featured}.

>>>>

The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria. The majority of the data (as implied by the project name) are taken directly from \hst{} Legacy Surveys, all of which primarily use imaging from the Advanced Camera for Surveys (ACS). Results from the individual surveys have been combined into a single photometric and morphological database, the Advanced Camera for Surveys General Catalog \citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in Table~\ref{tbl:gzh_numbers}.

@@

In the ACS-GC \citep{gri12}, individual galaxies are identified using a combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting framework \galapagos{} \citep{bar12}. GZH includes all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).

@@

The majority of the data in Legacy surveys described in \S\ref{ssec:legacy_surveys} had images in only one or two filters available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo impossible. For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two. Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).

@@

To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask was applied that preserves the color balance for galaxies, but desaturates the speckled noise against regions of blank sky. This technique was applied only to the coadded Stripe~82 and the COSMOS images.

@@

GZH also includes a set of images designed to measure the effect of active galactic nuclei (AGN) on morphological classifications. Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic or distort the identification of a bulge component. The presence of an AGN is simulated by modeling the point spread function (PSF) of the telescope and then inserting a bright source near the center of a real galaxy. For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generates 15~images with different simulated AGN for each host.

@@

For galaxies which have published redshifts from multiple sources, the following algorithm is used to select the $\tt Z\_BEST$ quantity. This first priority is spectroscopic redshifts; these are provided in the ACS-GC \citep{gri12}, 3DHST \citep{mom15}, and MUSYC \citep{car10} catalogs. A high quality spectroscopic redshift in the ACS-GC is the primary option; if none is available, then $\tt Z\_BEST$ uses the spectroscopic redshifts in 3DHST, and then MUSYC. For galaxies with multiple spectroscopic redshifts, more than 98\% are consistent at $\Delta z<0.001$, and so the order of selection makes no practical difference. If no spectroscopic redshifts are available, the 1-$\sigma$ errors of the photometric \citep[ACS-GC, 3DHST, MUSYC, UltraVISTA;][]{ilb13} and UltraVISTA grism data are used to select the redshift with the smallest error. Table~\ref{tbl:redshifts} shows the results of this selection.

@@

Photometric and spectroscopic data for the SDSS Stripe~82 galaxies are taken from the CasJobs DR7 tables. This includes $ugriz$ Petrosian magnitudes and fluxes, as well as the relative de~Vaucouleurs and exponential fits from the model magnitudes. Redshifts used for the SDSS galaxies are all spectroscopic. 82.6\% of galaxies in the single-depth images and 65.1\% of galaxies in the coadd images have a measured DR7 spectroscopic redshift.

@@

{\note Describe the GZ interface and the hierarchical decision tree.}

@@

The previous versions of Galaxy Zoo morphology classifications \citep{lin08,wil13} were based on observations of galaxies in the Sloan Digital Sky Survey (SDSS) which have a median redshift of $z<0.2$. In these cases, it was assumed that there was no cosmological evolution of the morphologies of galaxies and therefore any observed changes in the distribution of galaxies with different consensus morphologies was due to the effects of redshift on the image quality (\ie. the reduction in physical resolution, surface brightness dimming, etc). For both previous releases of GZ morphologies, a correction for redshift-dependent bias was applied based on matching the classification fractions at the highest redshfts with those at the lowest redshift. \citet{bam09} and \citet{wil13} provide complete descriptions of the process for GZ1 and GZ2, respectively.

@@

%The selection criteria for the different morphological categories is summarized in Table \ref{tbl:morphologies}. 
The surface brightness selection ($N_\mu = 3$) for the FERENGI galaxies was (1) low: $\mu > 21.5$~\magarc;  (2) mid: $20.5 < \mu < 21.5$~\magarc; and (3) high: $\mu < 20.5$~\magarc. For each of the four ``target redshifts'' ($z_\mathrm{sim} = 0.3, 0.5, 0.8$ and $1.0$), the images were redshifted in $\Delta z = 0.1$ bins up to $z_\mathrm{sim}=1.0$.

@@

\begin{table}
\caption{Summary of FERENGI artificial redshifting \label{tbl:ferengivalues}}
\begin{tabular}{lccccr}
\hline\hline
$z_{\rm sim}$ & $N_{z {\rm bins}}$ & $N_{\rm evolution}$ & $e_{\rm max}$ & $N_{\rm galaxies}$ & $N_{\rm images}$\\
\hline
0.3              & 8                  & 7                   & $-3.0$        & 72             & 4032 \\
0.5              & 6                  & 4                   & $-1.5$        & 72             & 1728 \\
0.8              & 3                  & 3                   & $-1.0$        & 72             &  648 \\
1.0              & 1                  & 3                   & $-1.0$        & 72             &  216 \\
\hline\hline
\end{tabular}
\end{table}

@@

The change in bias as a function of $\mu_r$ and \zsim{} is measured using the \ferengi{} images over all the evolutionary correction factors. It is assumed that the ``true'' (ie, debiased) vote fraction $f_{\mu,z}$ for a galaxy can be expressed as:

@@

GZH uses the values of $\zeta$ for \emph{all} sets of artifically redshifted galaxies to fit the overall distribution as a function of surface brightness, since the correction being applied is expected to vary as a function of the intrinsic galaxy properties. The galaxies that can be used to measure the calibration are restricted to those with a non-zero $f_\textrm{features}$ at $z_\mathrm{sim}=0.3$ and with a reasonable fit ($\Delta \chi^2 > 3.0$) to the exponential model for the measured change in \ffeatures.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{figures/eye_of_sauron.pdf}
\caption{Surface brightness as a function of redshift for 3,950~\ferengi{} images and the 102,548~galaxies in the ACS sample ith measured $\mu$ and $z$ values. The color histogram shows the number of \ferengi{} images as a function of $\mu$ and $z_{\rm sim}$. White contours show counts for the full ACS sample, with contours starting at $N=1000$ and separated by intervals of 1000 up to 7000.} 
\label{fig:sb_redshift}
\end{center}
\end{figure}

@@

Figure~\ref{fig:p_vs_p} shows that the relationship between \pfeaturesz{} and \pfeaturesrest{} is \emph{not} always single valued; hence, it is not appropriate to correct galaxies that lie in certain regions of surface brightness/redshift/\pfeatures{} space. These regions tend to have low \pfeatures{} values at high redshift, but a wide range of values at $z=0.3$. These regions contain two morphological types of galaxies: the first set are genuine ellipticals, which have low values of \pfeatures{} at both high and low redshift. The second group are disks whose features become indistinct at high redshift; hence their \pfeatures{} value at $z=0.3$ may be quite high, while the value observed at high redshift is very low. This effect is strongest at high $z$ and low $\mu$, where features become nearly impossible to discern in the images.

The criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, the relationship between \pfeaturesz{} and \pfeaturesrest{} is modeled by fitting the data with a polynomial of degrees $n=3$, 2, and 1, and using the best fit out of the three. These fits are shown as the dashed black lines in Figure~\ref{fig:6a}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between \pfeaturesz{} and \pfeaturesrest; this is quantified by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore \pfeaturesz{} cannot be boosted to its \pfeaturesrest{} value. Galaxies in this region are referred to as the \emph{lower limit} sample. These regions are highlighted in blue in Figure~\ref{fig:6a}. Uncolored (white) regions of the plot have sufficiently high slopes to consider the relationship as single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section~\ref{ssec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies are considered to have ``not enough information'' to determine the \pfeaturesz{} and \pfeaturesrest{} relationship, colored gray in Figure~\ref{fig:6a}.

The unshaded regions in Figure~\ref{fig:6a} define discrete ranges of redshift, surface brightness, and \pfeatures{} a galaxy must have in order for the debiased correction to be confidentely applied to a galaxy in the GZH sample. While the appropriate correctable regions were defined discretely, the true correctable region is assumed to be a smooth function of $z$, $\mu$, and \pfeatures{}. To define this smooth space, a convex hull is generated that encloses the correctable and lower-limit \ferengi{} galaxies in $z$-$\mu$-\pfeatures{} space. The boundaries are then adjusted until the contamination from both groups is minimized. The resulting hulls define the correctable and lower-limit regions for categorizing the \hst{} galaxies. The results of this method and final categorization of the \hst{} sample is displayed in Table~\ref{tbl:hubble_debiasable}. Of the galaxies at redshift higher than $z=0.3$, 17\% can be debiased using the $\zeta$ method, 27\% cannot be debiased, and 56\% cannot have the potential for a correction determined, due either a lack of redshift for the host galaxy or insufficient \ferengi{} images corresponding to the relevant $z$-$\mu$ values.

@@

\subsection{Challenges of debiasing questions beyond ``smooth or features''}
\label{ssec:higher_order_tasks}
As with the HST images, each FERENGI subject has a varying number of users answering the various questions in the hierarchical decision tree. Every user answers the first question, {\it ``Is the galaxy smooth and rounded, with no sign of a disk?''}; as such the vote fractions $p_\mathrm{smooth}, p_{features}$, and $p_\mathrm{artifact}$ are all computed with the minimum statistical error for any question, with roughly 40 total answers (see Section~\ref{sec:interface}). The number of users to answer any subsequent question, however, is always equal to or less than the number to answer the preceding question. The average number of responses per task for fourth- or fifth-tier questions such as spiral arm structure (Tasks 12--14) is only $4\pm4$ for the FERENGI sample; while this is distribution is strongly bimodal (reflecting the true morphologies of selected galaxies), the very low absolute numbers of votes introduce very high variance when attempting to calculate a statistical correction.

@@

%\begin{figure*}
%\center
%\includegraphics[width=\textwidth]{figures/hubble_z_mu_p_distributions.pdf}
%\caption{Distributions of redshift, surface brightness, and $p_{features}$ for correctable (purple), lower-limit (green), and NEI (pink) galaxies in the full GZH sample. The lower-limit galaxies have higher redshifts, slightly lower surface brightness, and lower values of $p_{features}$ on average than the correctable galaxies. The long tail of NEI galaxies in redshift and surface brightness demonstrates the limits of the \ferengi{} sample, for which there is no data at $z>1$ or $\mu>24$.}
%\label{fig:z_mu_p}
%\end{figure*}

@@

\section{The GZH catalog}\label{sec:results}

The data release for GZH includes morphological data for 181,101~images (generated from a total of 150,771~unique galaxies). The full table can be accessed at \url{http://data.galaxyzoo.org}. The online data also includes a secondary metadata table, which is drawn from a variety of sources detailed in Section \ref{sec:data}.

@@

The GZH catalog is corrected for classification bias only for the first question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks {\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this question, the catalog provides the additional parameters $\tt debiased$, $\tt lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$ fraction for $p_{features}$is chosen based on the categorization of the galaxy: if it is ``correctable'', $\tt best = debiased$, if a lower limit, $\tt best = lower~limit$, and if neither, $\tt best = weighted$.

The debiased and best vote fractions for $\tt p_{smooth}$ were calculated on the critera that vote fractions for all answers must sum to unity, such that:

\begin{equation}
p_\mathrm{smooth} \equiv 1 - p_\mathrm{features,best} - p_\mathrm{artifact}.
\label{eqn:nonlinear}
\end{equation}

\noindent In rare cases ($<1\%$ of the sample), this requirement resulted in negative vote fractions for $p_\mathrm{smooth}$; these were cases in which the $p_\mathrm{features}$ vote fraction was boosted to a high value relative to the $p_\mathrm{artifact}$ vote fraction. In these cases, the constraint that the vote fractions must sum to 1 is met by setting $p_\mathrm{smooth}=0.0$ and decreasing $p_\mathrm{features}$ accordingly. This correction is typically small, with a median decrease/increase of $p_\mathrm{features}/p_{smooth}$ of $\Delta p = 0.04$.

@@

In GZH, volunteers answer questions about a galaxy's morphology in a decision tree format. With this structure, questions shown to a user are dependent on their answers to the previous questions. For example, a user is only asked Task 11, {\it ``How many spiral arms?''} if they had answered ``yes'' to Task 10, which asks whether any spiral arms are present. This structure is used to reduce the workload of the users by only asking questions relevant to the particular galaxy; in this example, it would not be useful, nor would it make physical sense, to ask a user how many spiral arms in a galaxy which they had declared had no spiral arms to begin with. Figure~\ref{fig:decisiontree} shows the possible paths available for answering the questions offered in GZH. The colors represent the tier level of Tasks, which indicate the number of previous Tasks the given Task is dependent upon. The arm-number question, Task 11, is a 5th tier Task, meaning that whether this question is seen by a user is dependent on four Tasks preceding it. In this case, it is only shown to volunteers who voted the galaxy was featured/disk-shaped in Task 01, not clumpy in Task 12, not edge-on in Task 02, and had spiral structure in Task 10.

@@

{\note Summarize the broad trends that are seen regarding the fraction of galaxies with various morphologies, how that relates to color, size, etc. Briefly discuss results as compared with literature and theory.}

@@

The second set of plots in Figure~\ref{fig:comparisons} indicates that \podd{} is largely an effective method for separating irregular and/or peculiar galaxies from spirals. Despite the somewhat vague wording of the {\it ``anything odd?''} question in GZH, the AEGIS, COSMOS, and GOODS all show a marked increase in the irregular fraction increasing with \podd. Any threshold value for distinguishing between the two, however, depends strongly on survey/redshift~range.

@@

Of the 11,157 galaxies in the GOODS-N and GOODS-S full depth sample, 4,461 of these are in the shallow-depth sample. Figure~\ref{fig:shallow_vs_full} shows a strong correlation between $p_\mathrm{features}$ for both sets of images. The mean change in $p_\mathrm{features}$ from the shallow to full depth images  $p_\mathrm{features,full} - p_{features,shallow} \equiv \Delta p = 0.00$, with a standard deviation of $\sigma = 0.17$. While there is some variance in $\Delta p$ in the whole sample, the change is usually small and not often significant enough to change a morphological classification. Defining a clean sample of disk galaxies as those with $p_{features,best}>0.8$, elliptical galaxies as those with  $p_{smooth,best}<0.2$, and intermediate as those in between, 75\% of the sample would not change morphology. Of the remaining 25\% that would change morphology, only 0.3\% (representing 10 galaxies total) drastically change morphology from smooth to featured or visa versa, while the rest would transition to or from the ``intermediate'' morphology. Details can be seen in Table~\ref{tbl:shallow_to_full_stats} and examples of images representing the 9 possible changes (or lack of) in morphology are shown in Figures~\ref{fig:shallow_smooth},\ref{fig:shallow_intermediate}, and \ref{fig:shallow_featured}.
